---
title: "analysis for my_rf_cv"
author: "Hadi Nazirool Bin Yusri, collaborated with Muhammad Anas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This RMarkdown file interprets the function of my_rf_cv and its results.
- This function predict output \code{body_mass_g} using covariates \code{bill_length_mm},
\code{bill_depth_mm}, and \code{flipper_length_mm}.
parameter: k- the number of folds
The function returns the numeric with cross validation error.

```{r}
my_penguins <- my_penguins %>% drop_na()
mse_mat <- matrix(nrow = 90, ncol = 2)
ks <- c(2, 5, 10)
for (i in 1:3) {
  k <- ks[i]
  for (j in 1:30) {
    mse_mat[(i-1)*30+j, 1] <- k
    mse_mat[(i-1)*30+j, 2] <- my_rf_cv(k)
  }
}
mse_df <- data.frame(names = mse_mat[,1], mse = mse_mat[,2])
ggplot(data = mse_df, aes(group = k, x = k, y = mse)) +
  geom_boxplot(fill = "yellow") +
  labs(title = "MSE based on Folds", x = "Number of Folds", y = "MSE") +
  theme_bw(base_size = 15) +
  theme(plot.title =
          element_text(hjust = 0.5),
        text = element_text(size = 10))
mse_k2 <- (mse_df %>% filter(k == 2) %>% select(mse))$mse
mse_k5 <- (mse_df %>% filter(k == 5) %>% select(mse))$mse
mse_k10 <- (mse_df %>% filter(k == 10) %>% select(mse))$mse
mse_stat <- rbind(c(2, mean(mse_k2), sd(mse_k2)),
                       c(5, mean(mse_k5), sd(mse_k5)),
                       c(10, mean(mse_k10), sd(mse_k10)))
```
```{r}
mse_stats_df <- data.frame(k = mse_stat[,1],
                           mse_mean = mse_stat[,2],
                           mse_sd = mse_stat[,3])
kable_styling(kable(mse_stats_df))
write.csv(MSE_data, "../Output/Results/mse_data.csv")
saveRDS(MSE_table, "../Output/Results/mse_table.RDS")
```

Explanation: from the boxplot, we can see that the number of folds = 2 records
the highest mean among all three observations. However, the box is stretched
to its biggest width among all three, which also can be seen in the table where 
2 folds record the highest standard deviation of 6296.5 whereas the lowest 
standard deviation is recorded in 10  folds with 2433.0. This is the expected case
as smaller number of folds tend to be collected in a large group which also
include extreme values that stretches the mean and increase the
variability of the data. Higher number of folds means that most observations
are categorized based on approximated placement in the graph which means
that the mean of every fold is lower due to lack of extreme values. Hence,
this lack of variability also decreases the standard deviation that explains the
distribution patterns in the data folds.
